% !TeX root = ../AnalyticStacks.tex

\section{\ufs Berkovich spaces (Clausen)}

\url{https://www.youtube.com/watch?v=fnEPiDIF9_k&list=PLx5f8IelFRgGmu6gmL-Kf_Rl_6Mm7juZO}
\renewcommand{\yt}[2]{\href{https://www.youtube.com/watch?v=fnEPiDIF9_k&list=PLx5f8IelFRgGmu6gmL-Kf_Rl_6Mm7juZO&t=#1}{#2}}
\vspace{1em}

\begin{unfinished}{0:00}
"So, we're nearing the end of the course, actually. And, at the very beginning, in the first lecture, I kind of gave an introduction to what we wanted to have out of this theory of analytic stacks. In particular, I was putting some emphasis on the fact that we want to know that traditional frameworks for analytic geometry can fit into this perspective of analytic stacks.

We've sort of already discussed attic spaces and a little bit of geometry over this, the little bit of things like like tape curves. But what I want to add there was this issue of shifting, and then the idea was that you have to define some kind of derived attic spaces. This will not explain in full what is Uber Uber set up and in your formul. Maybe there are different ways to do it. I'm not sure it's possible. There are different ways to do it, yeah. So, this is yet in progress already. You, yeah, let's say that or something. 

The it's in Juan Estaban's paper on the analytic the ramstack that's okay. So, there you go. All right, okay. So, what I want to start moving towards today is a relation with Berkovich spaces. But, before discussing that, I want to just do a little bit of setup.

First, I want to talk about different Notions of how to localize an analytic stack over a topological space. So, well, we've already actually seen one way. If we have an analytic stack, and if we have S, which is maybe let's say a metable, finite dimensional, compact Hausdorff space, or it could be a maybe a locally compact Hausdorff space, which is locally one of these, then we've seen that that can also be viewed as an analytic stack. We can also view it as an analytic stack, and then we could just ask for a map F from X to S in the category of analytic Stacks. We discussed kind of what structure you get on X, basically you get a bunch of idempotent algebras in D of X corresponding to the closed subsets of S, or you can think in terms of the complementary opens as well, and you get sort of some idempotent coalgebras which would be like the J lower shrieks of the constant sheaf on the open subset, as opposed to the like I lower stars of the constant sheaves, giving you these idempotent algebras. But, in any case, you get a whole bunch of algebra objects in here which kind of let you localize this category over the topological space S.

But, we're going to want to, when discussing the relation with Berkovich spaces, it's going to be too annoying to require these kinds of conditions, even though they're satisfied in practice. So, I just want to discuss something slightly more general, some more general notion of how to localize an analytic stack along a topological space and the relation with this one in the case where you do have a metrizable, finite dimensional, compact Hausdorff space."

See, when I make the definition that I'm interested in, it doesn't matter whether it's a set or not. Question: the monom, if I only consider an that's like taking connector component. Exactly, yeah, so it just means that if you do the fiber product, then the diagonal, I mean the diagonal map associated to this inclusion is an isomorphism.

Okay, right, so and then of course a topological space also gives rise to a local. But let me actually change perspectives and just say 'S' is a local instead of saying 'S' is a topological space. Then we can ask for a map of locals, Lo(X) to S. Whether or not this is a set, this is some data that makes honest mathematical sense, because you're just saying that for every open subset, you have to give such a monomorphism, and you know unions have to go to unions and finite intersections have to go to finite intersections.

In the literature about locals, I don't remember, I didn't, don't use much, but this is like the direction of M of too, but I don't know when they define M of locals, is it in the other direction or in this? Yeah, I don't know either, so I'm doing the geometric morphism, let's say a geometric morphism of locals. Well, morphism of sites goes the other direction, you, the morphism of sites goes the other direction. Then I mean, yes, so I mean, I'm talking about a geometric morphism, but also of goes in the direction. Oh, maybe, oh, I forgot, yeah, yeah, okay, yeah, okay, go in the same direction. Okay, not, it's not used much.

Anyway, okay, but we can also ask for a stronger property, so that each inclusion of open subsets, say 'V' inside 'S', maps to, so it's supposed to give some monomorphisms, so maybe I should give some name for this, like 'f' or 'Pi', maybe. So this goes to like 'Pi' inverse 'U' subset 'Pi' inverse 'V' subset 'X'. We could ask that these inclusion maps are actually open immersions from the perspective of the six funter formalism that Peter discussed last time, the extended six funter formalism on analytic Stacks. So we could ask that each of these inclusions be shable, and that they be well chromologic smooth.

But in the case of a monomorphism, then it's quite easy to see that the dualizing object is canonically just the unit, and it's the same thing as an open immersion. A general monomorphism, I mean, it could look like anything really, it could look closed, it could look open, it could look like some mix. But it's reasonable to ask for this stronger property, that what looks like an open immersion on the level of the topological space is also, is looks like an open immersion from the perspective of the six funter formalism.

In the case where 'X' is a metric, finite dimensional, compact, Hausdorff space, can ask for, as before, 'S' to be an analytic stack.

What does this imply? Well, basically, you can just check on the level of the analytic stack associated to such a guy that every open inclusion, um, actually is an open inclusion from the perspective of the six functor formalism. Peter more or less discussed this last time, that our six functor formalism on analytic stacks, when we restricted to this case, recovers the usual six functor formalism on locally compact Hausdorff spaces. And then this property of being an open immersion is stable under base change, so that's, um, uh, and uh, you get the, yeah, so can you say so you know that open immersion holds for, ah, it is stable under, um, of analytic stacks or, well, uh, pullback, yeah, it's stable under pullback.

Yeah, um, so yeah, so this is the strongest condition. So if you have this, you can ask whether this holds. You just check whether certain inclusions or open immersions, if you have this, you can ask whether this holds. That's, as we discussed, uh, the last couple of times, that corresponds to some connectivity condition on the, on the ítm potent algebra, as you see, um, okay. Let me give a small example.

The second one is just given off by, lo, is just one of open, opener, yeah, that's true, yeah. So, yeah, so right, so you could think of this in terms of there's, lo, local X, and then there's some quotient local which is like the local of just monomorphisms that are open versions with respect to the six functor formalism, and then the second bit of data is a map like this, um, yeah, thanks for that remark, Peter.

Uh, and is it the case that the union, maybe I go confus, union of open immersions is an open immersion or to make it an open, yeah, no, no, that that's true, that it's an open immersion, yeah, which is needed to, well, it's needed to, yeah, it's needed to have this local, I mean, yeah, so, or well, remote, I mean, depends on how your, whe, right, right, right. No, but it's true, so that if you have a, yeah, a union of open immersions, then it's still an open immersion, and that's an important point to check when you're discussing these things, um, and it follows from this extension procedure for six functor formalisms that Peter discussed.

So if you have a union along open immersions, then those are sheafable maps, and but it's also a cover, and so you can you can get a a lower shriek map defined on the union and then you can actually check locally that it's comically smooth, um.

Okay, uh, so let's give an example. Um, so, well, remember way back when when we had Hub Pairs and stuff like that, so let's see, um. Then, uh, we assign to this an analytic ring, R, R plus solid, um. Then, we can take its spectrum, um, and then we can look at the local associated to this. And what we essentially already saw was that this, this analytic stack localizes along the usual, um, usual Huber topological space of continuous valuations.

No, you, you, ah, now you consider the spec in your, in your, yeah, this is this is what this is, spec n. So, Peter, yeah, I'm lazy, so I, yeah, I'm lazy, so I just say spec and, and then, uh, spies in the old sense, yes, it's a topological space, yes. And then, okay, the local, okay, and then you have a map of, oh, yeah, this loc, this means for every open in the add space, you give a monomorphism of analytic stacks, and uh, this, of course, this involves passing to some derived pairs in some sense, yeah, so because you are not, but your original pair is is not right. So if on the level of rational opens, this is just going to give another apine, uh, analytic stack, which is the one where you enforce, uh, that F invertible, just in the world of analytic Rings, you enforce that F is invertible, and that G1 over F, etc., GN over F is solid, um, and that defines some, uh, that
Can always refine any open cover here so that, so in fact, you get an open cover. So in fact, we showed, without having the L, without having introduced the language for it, we showed that any open cover or cover of a rational open in $\R^+$ pulls back to an open cover, can be refined to, pulls back to an open cover of, you know, the, pulls back under $\Pi$ to an open cover in the sense of the six functor formalism.

No, so let me make a remark. So let me make an open cover to cover by monomorphisms, yeah. So let me, let me make a remark. In general, it's not true that a rational open pulls back to an open immersion. Is there a proof of this? Oh, yeah, I'll give an example right now.

So, I don't know, have two formal variables, maybe $p$ and $X$. Oh, sorry, I should say just $\Z_p$. Yeah, that's, yeah, I don't need two variables. Thanks. So just one formal variable and then invert it. So what does this correspond to? On the level of analytic rings, we get this, and on the level of derived categories, this is just solid $\Z_p$ modules, and then this is just a, well, this is just algebraically inverting $p$. So the left adjoint here is just the inclusion of the full subcategory, or the right adjoint here is the inclusion of the full subcategory where $p$ is invertible.

So this passing from $\Z_p$ to $\Q_p$ is just algebraically inverting $p$, yeah, $p$ is a prime. And that actually, from the perspective of the six functor formalism, is a closed immersion, not an open immersion. That's a proper map because the, this hasn't the second variable hasn't changed, so we're just changing the underlying ring and not the analytic ring structure. But it's also a, yeah, proper monomorphism, it's a, it's a closed inclusion, it's closed, not immersion, not open.

So, I think we treated the case of some covering given by a function like $f$, like the Laurent cover, yeah, the one where $f$ or $1-f$ is less than or equal to mean, this kind of basic cover. And for those, is it the case? Yes, so then let me make another remark. However, if $R$ is Tate, then indeed, this doesn't arise. So in general, the problem is exactly these open covers in the Huber sense, which are just given by algebraically inverting a function without enforcing any inequalities. But in the setting of a Tate Huber pair, then you know, if you want to invert something, it's, the subset where you invert something can always be written as a union of subsets obtained by forcing inequalities.

So, it is not quasi-compact in general, right? But dealing with something which is in the sense of the ADC space is quasi-compact because it is a rational domain. I think in the, yes, but I mean, it is Rush, so it is quasi-compact in the, yes, in the. This also has to do with the fact that we didn't directly, I was sliding one little thing under the rug here, which is we didn't really directly define this as a map. We didn't really directly define it like this, remember we actually had this valuative spectrum of all of these guys, and we actually defined this map and then we used Huber's retraction here. So this was not quite accurate, because that would be accurate on the level of $\mathrm{Spa}$, but that's not exactly how we get it for $\mathrm{Spa}_a$. Instead, we, just assume that the real $\mathrm{Spa}_a$, yeah, okay, right, right, yeah. The idea is open, and then it's okay, yeah.

So, the point is that the rational opens in the Tate case can always be described by forcing inequality among the valuations. Okay, yeah, let me just try to finish what I was trying to say. It's like, I don't know, this is very, I just, just to give an idea of what's going on, I don't want to get too precise about it, but it's this kind of phenomenon, where these guys correspond to this kind of thing, which does correspond to an

So, sheets on this $F$ is not there. In fact, you cannot algebraically invert $F$, but using the right-hand side. That's right.

Okay, and also, there is another topology on the same space, with the same constructible subsets. Where the open pulls back to open.

So, another fix, even outside the Tate case, is to choose a slightly different topology from the one Huber described, where both of these things are open. It's not the constructible topology, no. It's a topology which is incomparable to the Huber topology. For this subset here, $P \neq 0$, it will be closed from one perspective and open from the other perspective. It's open from Huber's perspective but will be closed from the perspective of this other topology.

It is a spectral space. To be open, you basically redeclare Zariski open subsets to be closed, which the Zariski open they are not.

For example, inverting $P$ here, inverting $P$, is now closed in the new topology. We haven't discussed that element of synthetics so far, that's true. But let's leave that aside, I think there's already enough information being discussed.

Is it the opposite spectral space? No, it's not the opposite spectral space, because these ones are still the ones where you're enforcing inequalities like $f \leq 1$, that's still open in both cases. It is the opposite of one of the ones Huber describes in one of his papers.

Yes, we can make this more precise. I'm going to hesitantly say yes, it's obvious if you remember the definitions of everything. Maybe we need compact or not, because I mean, you want an input to correspond to it, but I'm not sure whether if it's not quasicompact, you have...

Yeah, so everything is defined by inequalities $f_i \leq g_n, g_n \neq 0$, and this one you replace by saying that is a closed condition for any $G$. Well, I mean, you have a rational open, so the conditions are satisfied, like the ideal generated by all of them is open. So, you can't just invert $G$ if that doesn't correspond to a rational open in Huber's sense, but in situations where you can, it corresponds to a closed conclusion.

One last remark about this general setup: if $S_i$ is some inverse system of compact Hausdorff spaces, then giving compatible maps from $\operatorname{Lal} X$ to $S_i$ for all $i$ is equivalent to giving a map from $\operatorname{Lal} X$ to the inverse limit. And it's the same for $\operatorname{Lo}_p$. If all of those ones factor through $\operatorname{Lo}_p$, then this one will also factor through $\operatorname{Lo}_p$.

Every compact Hausdorff space is a limit of metrizable finite-dimensional spaces, potentially in many different ways, but in many situations, there's a natural way of doing it. We'll see this in the setting of adic spaces, and then this gives you a way of going from the case of metrizable finite-dimensional compact Hausdorff spaces where you can sometimes go from this perspective and you can go to this perspective.
You're closed, you know, the situation kind of passes to inverse limits in a nice way, and um, but now you no longer have to worry about things being metrizable or finite-dimensional. Okay, that was my little um, just uh, is a map to s the same thing as a map from loal? No, because you have this connectivity condition, so it's the you still have to impose this locally that locally all the item poent algebras are connective, so yeah. I mean, as far as I, it's not like I produced a counter example, but I I I kind of believe that it's not the same, uh, okay.

Okay, so I'm always confused, is there really a t-structure def over D of that object? And no, no, there's no t-structure. So what I didn't, I don't have to say what I mean by connective. I have to say what I mean by connective locally, and what I mean by connective locally is that there exists a cover by apine things such that it's your object when you pull back to each of those apine things is connective. Now, once you're in the apine world, connectivity is a pullback of something connective, is you have a t-structure and the pullback of something connective is connective, so it's kind of. And also, if the pullback is connective, then it's connective or not, no, that that is not necessarily true, okay, okay.

Okay, so it's not like, so it's not a sufficient condition for having a. So this is like the for schemes that you have the the non-aine orens, but still, if you use as the flat or pqc, still if it's up upstairs, it's up downstairs, so that's. But in your topology, of course, you have much more stuff, yes, yes. So you can have these wheel-we things where, yeah, you have a map which is apine locally, but with an with a map with apine Target which is apine locally, but not globally, and this kind of, yeah, um, yeah, that's kind of unavoidable when you're doing analytic geometry.

So, uh, okay, um, where are we? Okay, so yeah, so um, so Banach spaces. So let me just start with a reminder on the definition, so we know where we're going. So, so, so, a this is a Banach ring. So what does that mean? It means that a is a commutative ring, and this Norm map from a to the non-negative reals, uh, satisfies, so first of all, uh, Norm of 0 equals 0, second of all, uh, the triangle inequality, Norm of x + y is less than or equal to the norm of X plus the norm of Y, and third of all, um, it's sub-multiplicative. So, um, and uh, probably have to put the norm of -1 is equal to the norm of one, which is e z, yeah, I should probably put that, yeah, so uh, either a equal Z or Norm of 1 equal 1 and Norm of us one, also do you need that? It does not follow, uh, I'm not sure how much it follows, but it, it's usually they want the triangle inequality Al with x + y, okay. I think you can, you can get it, you can give a crazy thing like the negative multiply by two, you can do something that still satisfy the a without, but of course, it would be equivalent something satisfying the a, this is probably not how to show, oh, okay, uhhuh, yeah.

Um, yeah, and then, so let's say that, and then a is a complete, uh, with respect to the norm, uh, um. So an example, yeah, there's, so example for, say, s is a compact hausdorff space, uh, you could take for a to be, uh, functions, say, I don't know, complex, uh, complex-valued continuous functions, and take the norm to be the sup norm, where you have the usual absolute value, um, and this, maybe this is kind of, uh, right. Another example would be if, uh, if R is a a Tate-Huber ring, um, and if you choose a pseudo uniformizer, uh, topologically nilpotent unit, uh, then you can define, uh, define a norm, uh, Peter actually wrote down the

Yep, this is multiplicative. It's not multiplicative in general.

Okay, so right, and then so to this data, so this to a and the Norm Huber assigned the space, which has a set Burkovich. Thank you, yeah, we're switching over now. Thought Burkovich, which as a set is given by the. Norm of $f$ equals $z$ if and only if $f$ equals $z$, right.

So, I'm just using this notation $X$, so kind of it's just a decoration to. And this is now a multiplicative seminorm, with which is bounded by the given Norm you have on the the Banach algebra $A$.

Well, for example, in and you can take. If you require that the norm restricts to the usual Norm on the complex numbers, then in fact these are all the examples. So that's maybe Gelfand's theorem. So, those are basically the only examples in this situation. And multiplicative includes the of Zero element, that is the norm of one is one, yes, yes, yes.

Except, but this is maybe zero multiplication of zero numbers, yeah, we don't want that. So, we want these to be like points, so we want them to be non-empty. So, we want one to be different from zero, I don't know, I mean, yeah.

But, do you allow $\Z_R$? No, well, wait, I allow, okay, I allow $\mathbb{A}$ is the zero ring, when this will be the empty set.

Okay, so, there's the, so this is actually a compact Hausdorff space. So, I didn't describe the topology, but here it is. You can view it as a subset of the product over all $F$ in $A$ of the interval from zero to the norm of $F$, and it's actually a closed subset. And this map just takes a norm and records its value on $F$, and the topology is just the subspace topology, so it's a compact Hausdorff space.

Okay, so what we're going to do is, we're going to move this definition, we're going to try to make the same definition to make the same definition, but in the world of analytic stacks instead of topological spaces. So, we want to take the same idea, which is that we want to look at the set of all Norms, multiplicative seminorms on $A$, bounded by the given Norm on $A$, but we want to say that in the language of analytic stacks and that we've discussed, using the notion of norm on an analytic ring that we discussed earlier, yes, yes, yes, that's true.

Okay, so let me remind you about this notion of a norm. So, the definition of, well, we could say even more generally in an $\infty$-category stack. A norm on $X$ is a map from the algebraic $\P^1_X$ to the closed interval from zero to Infinity, including Infinity, which is multiplicative away from Infinity. So, let's say on Norm inverse $0$ to Infinity, and let me just write it suggestively like this. You really should write down the commutative diagram with inversion on $\P^1$, inversion of the coordinate on $\P^1$ and inversion of this extended real positive non-negative real axis here. And some condition on how $\mathcal{P}$ sits, $p$, $p$, $p$, yeah, so this is the $p$, oh $t$, $t$ is the variable on $\P^1$, yeah, right.

Yes, what do you mean by how $\mathcal{P}$ sits? Yeah, so, remember $\mathcal{P}$ was this ring object you have over any analytic ring, which is the free guy on a topologically nilpotent element. And it's some version of a unit disc, and what we ask is that this Norm function gives

Small $a$ map in the category of analytic Stacks. Yeah, so these objects are fixed, right? When you fix $X$, this is fixed, and this is fixed. Yes, that you know that there is a. Why was it? Well, we basically by definition, every analytic stack was a small co-limit of representable analytic Stacks, okay? You have a.

Because there was a notion of analytic ring where there is the category, yeah. Okay, there, there, you, you, you handle the problem of large sizes. I mean, because it's enough to check the condition some smoke, but then you have the analytic stack where you cover, but you don't know which covering you need to give a ism, so you have need all possible covers could be covers by bigger and bigger see, but you say the category is accessible. Yeah, so the, the, the main technical result you need to prove is that the sheifification of an accessible prief is still an accessible prief. That's the main technical result you need to prove. We did not discuss this at all, but that's what's underlying the resolution to these issues. It's like in Waterhouse.

Okay, so this, in fact, so there's a cover, so this gaseous base maps to $n$. In other words, you can write down a norm on this gous space tack, and it's, and this, so this, and this is actually the universal norm on an analytic ring with a variable $Q$ in $R$ such that norm of $Q$ is precisely equal to $1/12$. What did you write? $NX$ is the analytic stack $n$, $n$ is an analytic stack. Yeah, so the, so $NX$, the set of norms, is actually just the set of maps from $X$ to some stack $n$.

Right, so yeah, so if you ask for a norm on an analytic ring and an element whose norm is exactly equal to $1/2$, which is kind of a somewhat stringent condition, because a priori again, the norm map is norm of $Q$ is a map from $Spec R$ to $[0, \infty)$, and you're asking that it factor through this, a priori, its image could be some interval or something, but you're asking that its image be exactly this singleton. The universal example of that is this guy, and moreover, the map to the base stack is actually a cover in the sense of our Gro de topology on analytic Stacks, because every norm on an analytic ring locally, you can find such an element. We had this argument, we discussed this two lectures ago. Right, everything here was like $X$ was a $Spec$ of an analytic rate. I mean, I made this definition for a general $X$, but it, I mean, it doesn't matter because the condition, I mean, the norms on an analytic ring, they satisfy descent basically. I mean, it's kind of follows from general nonsense, and so it automatically glues to say what a norm is on an arbitrary analytic stack, and it just unwinds to the same thing. So the cover also exists because it exists locally, like you GRE it. Well, the map, the map, no, the map exists because you can write down this norm, and then it's a cover because given any norm on an analytic ring, after a cover, you can find a $q$ that satisfies this property.

Sure, do you need to do some base tank? I'm sorry, do you need to do a base change? What do you mean? Is it okay, or you still have a question?

Okay, so I want to, before finishing the discussion of or introducing the definition of this enhanced Berkovich Spectrum as an analytic stack, I want to explore a little bit about so, what does $n$ look like? So, well, what do we have on $N$ if you have a norm on an arbitrary analytic ring? So, if you have a norm $p: R \to [0, \infty)$, so as mentioned, for any section here, you get a function from $Spec R$ to $[0, \infty)$, but over an arbitrary analytic ring, the only thing we know exist are the integers. So, given $n$ in $\Z$, we get a map which records the value of your norm on the integer $n$. So, what does this
We'll also see that the fiber over any point in the image is non-empty, so that at least in this case, maybe it's a general fact - I don't know, at least in this case, it's kind of a theorem that the image is closed, so to speak. Okay, right, so now note that the more traditional thing is this Berkovich spectrum of the integers, so that was also by definition a subset of this product going from zero to infinity, and it was given by those Norms, yeah, so multiplicative, avoiding Infinity, satisfying the triangle inequality.

Let me remind you what this thing looks like, in case people haven't seen this before. Recall that $\M(\Z)$ looks as follows: you have a point at the center, so to speak, which corresponds to the trivial Norm, meaning the zero Norm of Z is Z Norm, and the Norm of everything else is equal to one. Then, you have several branches. You have an archimedian Branch, so at the end of the archimedian branch, you have the usual Norm, the usual archimedian Norm, the usual absolute value. But then, for each prime P, you have another branch, which also ends at some point. To get the correct topology on embedding it into $\R^2$, you should probably make the branches get shorter and shorter and shorter, but okay, that's...

Yeah, but the situation with these p-adic branches is a little bit different. So, what's going on here? Here, you have the usual absolute value, and here, at the halfway point, you have the square root of the usual absolute value. And here, you know, then you can put any Alpha between zero and one, and you can kind of see from the intuitive perspective that this interpolates between the usual absolute value and the trivial absolute value. Here, what goes at the top is not the usual p-adic absolute value; the usual p-adic absolute value sits somewhere here, so normalized to say so that P equals 1 over p. And now, you can actually scale it to any positive real, and then there's also a limit as the scaling goes to infinity, and what that gives is the trivial Norm or the pullback of the trivial Norm on the residue field FP, so in other words, the Norm of any multiple of p is equal to zero, and the Norm of everything else is one.

Okay, what of course, no, I... Yeah, this is great. I think this was something like this, this is the first talk. There was a talk in this course, it was in this course or another, probably in this course, there was some discussion of, but maybe I could do this another thing. Yeah, so I'm trying to recall something which is well-known indeed, in order to set up the discussion of what's following here. So, but in particular, I want to emphasize this is a really big space, but the Subspace MZ is quite small, you know, one-dimensional.

So, now what we're going to see, so there, you allow the value to be in, but here, you don't. That's correct. So, here's going to be the claim: the image of the Norm is a larger subset. It looks like this: you have all the same ones as before, sorry, I'm trying to say that it stops there, trying to draw like a closed interval sign, but then also at the archimedian place, it gets extended. So, here, now the usual archimedian absolute value is also in the middle of the interval, and you can take arbitrary powers of it, so for any Alpha in R greater than zero, you can take powers of it. So, it'll go to there in one direction, and to the other direction, you get some really strange point, which corresponds to... So, it's a subset of there, so it's given by some maps from Z to the extended real line there, and it's given by Norm of n equals infinity if n is not equal to -1, 0, or 1.

To infinity and then compactified at the end. Yeah, I guess what I - you can try to write a formula for it. It's like the image norm is like - you take the Berkovich space of the integers. Ah, no, let me make a before I say this.

In particular, the triangle inequality can fail. Well, that's quite clear here - you have norm of one equal one, but norm of two equals infinity. Okay, that's a pretty drastic failure of the triangle inequality. But also, like for the square of the usual absolute value, which is a new thing, you have the triangle inequality fails as well.

So yeah, I guess another way of saying this is like the image of norm - you can get it from the Berkovich spectrum of Z. On the Berkovich spectrum of Z, you have an action of the real numbers greater than or equal to one. Wait, did I - yeah, or well, yeah. Um, or maybe, yeah, I don't know, but on this other thing, you have an action of the positive real numbers. You can kind of do this, and that doesn't do anything on the non-Archimedean branches, and then on the Archimedean branch, it extends it all the way, and then you compactify it - one-point compactification. So, I don't know.

Okay, right, so let's explore this and let's see what kind - what is kind of going on. So, let's consider just the map - what's that? Is the one-point, yeah, the one-point, yeah, yeah.

Question: The picture you seem to see this image gen topological space, but this is supposed to be something associated with Z, right? That's a good question. So, by definition, I made it a - I was saying it's a closed subset of the topological space. Now, you can view this as an analytic stack. We saw how to view this as an analytic stack, and you can take the product in the category of analytic stacks - that's perfectly legitimate. It's no longer finite dimensional - sorry, it is metrizable, it's no longer finite dimensional. So, we didn't quite talk about this thing, but you can still view this as an analytic stack, and you still do get a map of analytic stacks from N to this product, and this closed subset does correspond to a subanalytic monomorphism of analytic stacks here, and the map from N there does factor through that closed subset, and so you can view it in several different ways.

Okay, to explore this, so consider a fixed prime p, and consider just the norm of p. So, here's the first claim: we can understand the locus in this universal space of norms where the norm of p lives between zero and one. This is just the same thing as the stack parametrizing norms on which the variable p lives between 0 and 1 - let's call this N and Z less than absolute value of p less than one. This is equal to spec Qp, the Gauß version of the p-adic numbers, across this stack associated to the open interval from 0 to 1.

Yeah, well, in fact, this is quite easy to see because we know that the universal analytic stack equipped with some variable whose norm is between zero and one is spec of Zq hat plus or minus one Gauß cross 0,1. And then you just have to impose that that variable becomes p, so you just set q equals p or you mod out by q minus p, and then that, as Peter discussed when discussing this Gauß base stack, gives you some analytic ring structure on the p-adic numbers, and then the second variable doesn't really change.

And so, I'm claiming in particular that if you look at the universal - let's say we take the fiber over a point lambda in 0,1, then you get a normed analytic ring structure here. And it is - so what does that mean? It means that for every radius r, you have some notion of overconvergent functions on a disc of radius r, where the notion of on a disc of radius r is the usual one from non-Archimedean geometry, where you take the normalization of the absolute value on the p-adic numbers for which the absolute value of p is equal to this lambda. So, what we're seeing here is the kind of the interior of the p-branch here is kind of fairly...
Straightforward to understand. So, next, let's look at the locus where another locus that's fairly easy to understand is the locus where $p$ is between one and infinity, strictly between one and infinity, because that's the same thing as saying that $p$ has to be invertible. The absolute value of $p$ is away from zero, and then it's the same thing as saying that the absolute value of $1/p$ is between $0$ and $1$. We can again use the exact same argument to understand what this is, and what you get is you get $\text{Spec}(\R) \times [0,1]$, and the argument is the same. As Peter explained, if you take this ring and mod out by setting $q = 1/p$, then you actually get the real numbers. You get a certain analytic ring structure on the real numbers.

Again, if you look at the universal norm with a fixed value of $\lambda$, the universal norm here is the usual one given by convergent functions in Archimedean geometry, say complex geometry, but with respect to the norm, which is a power of the usual absolute value, where $\alpha$ is such that the norm of $1/p$ exactly gets $\lambda$.

I'm not quite sure where the over-convergent functions show up. You had some formal ring with $q$, but then you specified that it is the usual over-convergent functions. The first thing to understand, of course, is why when you take this ring and specialize to $q = 1/p$, you get the real numbers. That has to do with some kind of base-$p$ expansions.

Then you have to understand what the base change of the module $p$ is. It should be some module over the real numbers, some sequence space with some summability condition. You can see that the summability condition is basically just some exponential decay, as Peter described.

The point is that this thing does sit between the usual ring of over-convergent functions on the unit disc and the ring of holomorphic functions on the interior of the unit disc. When you do this over-convergent business, the subtlety of exactly what ring it is and what summability property you have doesn't matter anymore, and it just returns the usual ring of over-convergent holomorphic functions on the disc, with some scaling of the usual absolute value.

In particular, this locus is independent of $p$, because the universal norm didn't really depend on $p$. There's some rescaling property of the norm, but it doesn't affect this subspace of the universal space of norms. This is the kind of thing you need to see to understand that you're getting the Berkovich space. You have some infinite-dimensional space, but the conditions on the various prime numbers are very tightly related to each other, just like in the classification of norms on the integers.

Other and is determined each is set of norms on z. Yes, not up to equivalence. No.

Question: all the point right? Yeah, why that would be. Is there some explanation why that would be for me?

It's a bit of a calculation. I mean, in our axium for normed analytic ring, we had no version of the triangle inequality whatsoever. We just had this that the norm should be multiplicative. But then you can look and see well, if you believe what I'm claiming, then kind of almost all of it does almost all of the space does satisfy the triangle inequality because you can just check on in terms of the rings of functions that are being assigned, and you can just verify that the triangle inequality holds. So whenever you're in the ordinary Banach space of Z, you actually satisfy the triangle inequality, and then okay, it's a you get some sort of quasi-norm if you move out in this direction, and this part is a little funny, but if you throw that away, so there's always some version of the triangle inequality that is automatically satisfied just as a consequence of multiplicativity, and that's kind of funny.

Yeah, in the usual, the like, in fact, was consider earlier, then I mean, it's I'm speaking now about Urs classification, the or maybe, so you can put the following condition. I don't remember which reference, instead of inequality you can put like x plus y val less equal to some constant times x y, and then one can prove that after a normalization by some power, you have the triangle inequality or even the.

Yeah, and so is it the case that here you can is related somehow where, yeah, in the locus where, so if you know that the priority that the nor some integer like or three not infinity, then you can get the triangle inequality by scaling it.

Yes, exactly. Yeah, so if, well, I have on everything now, I'm speaking about Bierz. Like in the big, let me make some further claims.

Claim: if you have a normed analytic ring with the norm of 2 say, doesn't matter, less than or equal to 1, automatically satisfies the non-Archimedean triangle inequality. A normed analytic ring with norm of 2 less than or equal to 2 satisfies the usual triangle inequality. Oh, I sorry, let me move this, is the that no of 2 two is equivalent to no of 3 three, yes, yes. Two is an arbitrary prime number here, about to 6, is it that's also equivalent, yeah, yeah. So I guess prime is not so important, yeah, two, yeah, two is an arbitrary integer bigger than one.

Okay, so, and then, where am I now? Oh, yeah, so a normed analytic ring with norm of 2 less than infinity always, there always exists a constant C greater than zero such that the norm of x + y is less than or equal to C * the norm of X, the norm of Y, but this is interpreted not in the sense of normal functions, but it's not. Yeah, it's some universal thing, like, you know, you write down, you have whatever you have, yeah, you have P1, like, yeah, the locus where the norm of the T variable is less than or equal to a, cross P1, you know, locus for the S variable is less than or equal to B, um, yeah, that this maps to, so it's a and b are less than infinity here, so it's this maps to P1 R, and then this maps to Z Infinity, but this should factor through zero, and then C * a plus b.

Yeah, so, and this is addition A1, yeah, they, it's well defined because this happens to live inside A1, which we already argued earlier.

Yeah, yeah, so there's always some version of the triangle inequality, um, yeah.

How do you prove these claims? By the way, these claims imply the claim about what the image of n is, because, um, so, yeah, so, and then this extended Berkovich space, the one I mean the specific one that I wrote down, the reason is that you can, you can look at the norm of two, which goes to zero infinity, ah, yeah, if you want to, if you want to know the image of something, you can actually work, you can actually work on stratifications of your topologic, you don't have to work in closed covers or open covers, you don't have to work locally
Over the locus where $2$ is less than or equal to $1$, the locus where $1$ is less than $2$ is less than infinity, and then the locus where $2$ is equal to infinity. We then have to take the union of the images we see there and here. If you believe this claim, then there you have the non-archimedean triangle inequality. So, here it's automatically a subset of just by some universal argument, the non-archimedean Berkovich spectrum of $\Z$. We're contained in the claimed locus there. This thing we already classified is contained in the archimedean locus, the archimedean locus. So, the last thing we need to do is to see that this locus consists of just one point.

We need for all $n$ different from $0$, $1$, and $-1$. And that actually doesn't follow from the claims well. Yeah, well, the claim that these conditions are independent of $2$ does give this as well. The last thing you say plus be, that's true. You can also directly argue that if $3$, for example, wasn't sent to infinity, then you'd be in one of these loci, and then $2$ wouldn't be equal to infinity.

To prove these kinds of claims, you just calculate. For the first part, we only know it's not larger than once, and it's not implied directly. Then you also need to see that if you take any point and then take that, there exists some normed analytic ring which has those values. We already saw it for the points in the interior of the rays in the Berkovich space, and it's also quite easy to hit the center because you just do some non-archimedean geometry over some Laurent series ring with $\Q$ with the trivial norm, or you can hit the points at the end by doing some non-archimedean geometry with $\F_p$. This gives the containment, but you can actually see the other inclusion by just exhibiting.

To prove, we can assume we have this $\Q$ with a norm of $\Q$ between $0$ and $1$, and then we're working over this Gauss to base. For the first claim here, the non-archimedean claim, what do we need to do? Well, then the universal case, given that we fix this data, we're just asking that the norm of $2$ is less than or equal to $1$, so it just lives over an idempotent algebra. This was because of the claim that you have a cover. You can check things like the non-archimedean triangle inequality after passing to the total space of a cover.

This idempotent algebra is just the ring of holomorphic functions, so to speak, the overconvergent version of the unit disc, and then you just mod out by $T - 2$. This gives a power series or Laurent series with integer coefficients that converge to radius zero, which are converge on some unspecified open disc around the origin. This already shows that the condition is independent of $2$, and then you can just look at the universal over this and check the non-archimedean triangle inequality.

The only other locus you need to worry about is the locus where you're...
Between one and two, and then you're in this non-Archimedean branch, and we saw you get the usual thing: you have the triangle inequality there. And then, to prove this claim, it's actually enough to - I think it's easier to prove the root. The root is, it's easiest to prove this claim, and then that implies the claim, because this means that the only other possible point to consider, we're living in the Archimedean locus, so we're just some rescaling of the usual absolute value. And then, this weak triangle inequality, this quasi-norm triangle inequality, is actually satisfied.

To prove this, you again just do a calculation. It's sort of similar, except you're setting $t$ equal to 2, or you're setting the inverse of $t$ equal to some weird version of functions convergent on the open disc. And again, you just observe that it's independent of 2.

In this locus, your convergence property is shrinking down to zero. In this locus, the locus relevant to this claim, it's kind of the Laurent tails that are forcing the convergence out to the boundary of the unit disc.

As mentioned, there's no course this Friday, but please come here, and Peter will be here in person, and so will three other people giving talks, some of which are relevant to the material here. Next week, I'll continue this discussion of Berkovich geometry next Wednesday, and then the next Friday is actually going to be the last class, so we're really almost done here.

Regarding the question about the ontic stack sitting over the classical regions, and what it means if it sits over infinitely many points, it's a bit weird. The norm is quite different - it's an analytic norm, not the norm on a ring. This relates to the statement about the set of norms being like the rescaling of the norms and forming a stack, where any analytic space has a unique map to this stack.
According to the website, we have two more weeks. However, we may have to change that because there was some... Apparently, on the IHS website, it says we have two more weeks. But I'll get it fixed because the number of talks was originally more than the actual...

We did decide that next week is the last week, right Peter?

Yes.

What's that IASS?

Here, I see. In BOND classes, officially end, that's why we're stopping.

\end{unfinished}